Learning Network Size While Training with ShrinkNets

### 2018-01-06 paper/paper.tex
Margin adjustments
Title and rephrasing

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
\begin{document}
\title{ShrinkNets}

@@

The additional term $\lambda|\max(0, \theta)|$ introduces sparsity (see Lasso
loss~\cite{Tibshirani1996}). 
% The $\lambda$ parameter, that can take any
% positive value, adjusts how aggressively the network deactivates neurons, with
% larger values indicating more aggressive deactivation.
The second component of the loss, because it increases the gradient with
respect to $\theta$, pushes its value towards zero. Neurons with little impact
on the original loss (gradient lower than $\lambda$), will not be able to
compete against this attraction towards zero. Because the entries in $\theta$
with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
controls the number of neurons/channels in the entire network. We introduced
the $\max(\dots)$ into the loss to make sure that neurons are permamently disabled
when performing gradient descent based optimization. Next, we
explain how to implement ShrinkNets efficiently.

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
\includegraphics[width=\columnwidth]{convergence}
\vspace{-.2in}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\vspace{-.2in}
\end{center}
\end{figure}
\subsection{Does ShrinkNet find good networks?}

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
  \includegraphics[width=\columnwidth]{hyper_opt}
  \vspace{-.2in}
\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
\vspace{-.2in}
\end{center}
\end{figure}

>>>>

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
\begin{document}
\title{Learning Network Size While Training with ShrinkNets}

@@

The additional term $\lambda|\max(0, \theta)|$ introduces sparsity (see Lasso
loss~\cite{Tibshirani1996}). 
% The $\lambda$ parameter, that can take any
% positive value, adjusts how aggressively the network deactivates neurons, with
% larger values indicating more aggressive deactivation.
 The second component of the loss increases the gradient with respect to $\theta$, thus pushing its value towards zero. Neurons with little impact
on the original loss (gradient lower than $\lambda$), will not be able to
compete against this attraction towards zero. Because the entries in $\theta$
with a value of $0$ or less correspond to dead neurons, $\lambda$ effectively
controls the number of neurons/channels in the entire network. We introduced
the $\max(\dots)$ into the loss to make sure that neurons are permamently disabled
when performing gradient descent based optimization. Next, we
explain how to implement ShrinkNets efficiently.

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
\includegraphics[width=\columnwidth]{convergence}
\vspace{-.25in}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\vspace{-.2in}
\end{center}
\end{figure}
\subsection{Does ShrinkNet find good networks?}

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
  \includegraphics[width=\columnwidth]{hyper_opt}
  \vspace{-.25in}
\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
\vspace{-.2in}
\end{center}
\end{figure}
